---
title: "Cherry Blossom Q 10"
author: "Daniel Byrne"
date: "9/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(tidyverse)
library(mosaic)
library(gmodels)
library(knitr)
library(RColorBrewer)
library(lattice)
library(car)
```


## Analysis

```{r}
# Load data
files = sapply(1999:2012,function(year){paste0("./MensResults",year,".csv")})
load.files = function(fileName) {
  read.csv(fileName,stringsAsFactors = FALSE)
}
mensResults = do.call(rbind,lapply(files, load.files))

## Convert to number
mensResults$Age = as.numeric(mensResults$Age)

## Convert to factor
mensResults$Race = sapply(mensResults$Race,function(x) { 
  r = strsplit(x, " ")[[1]][1]
  return (r)
})
mensResults$Race = as.factor(mensResults$Race)
mensResults = mensResults %>% select("Race","Name","Age")
head(mensResults)
```


```{r}
plot(Age ~Race, data = mensResults, ylab = "Age (years)", xlab = "Race")
```

```{r, results = 'asis'}
stats = favstats(Age ~ Race,data=mensResults)
print(stats, type="html")
```

```{r}
bwplot(Race ~Age,data=mensResults)
histogram(~Age, data = mensResults)
```

```{r}
smoothScatter(y = mensResults$Age, x = as.character(mensResults$Race),ylab = "Age (years)", xlab = "Race Year", main=" Figure 4 - Smoothed Scatter of Race Year v Participant's Age")

```

## One-way ANOVA

We fit the one way analysis of variance (ANOVA) model, using all of the groups.

```{r}
densityplot(~Age,data=mensResults)
```

```{r}
densityplot(~Age,groups = Race,data=mensResults)
```

```{r}
anova(lm(Age ~ Race, data=mensResults))
```

The p-value provides some evidence that there ius a stistical difference between the mean age of participants over sucessive years of the race.  By default, the use of the linear model function displays the pairwise differences between the first group (Race 1999) and each of the other groups.


```{r}
summary(lm(Age~Race,data=mensResults))
```

## Pairwise Comparisons

The model table below displays the differences between the grand mean and the group means.

```{r, results='asis'}
results = model.tables(aov(lm(Age ~ Race,data=mensResults)))
results$tables
```


## Residual Analysis

```{r}
aov1 = aov(lm(Age ~ Race, data=mensResults))
plot(aov1,which=1,"Figure 5 - Residuals vs Fitted")
```

```{r}
plot(aov1,which=2)
```


```{r}
plot(aov1,which=3)
```


```{r}
#dw = durbinWatsonTest(lm(Age ~ Race,data=mensResults))
p <- ggplot(mensResults, aes(length, fill = )) + geom_density(alpha = 0.2)
p <- ggplotly(p)
```


